---
title: "Atida Task 2.2"
author: "HyeKyung Yoon"
output: html_document
---

```{r}
library(tidyverse)
options(width=100)
```

# Load Data
```{r}
email <- read.csv("q2_dataset.csv")
duplicated(email$event_date) #to check duplicate data
class(email$event_date) #to check data type (character)
email1 <- email %>% mutate(event_date=as.Date(event_date, "%Y-%m-%d")) # to change data type into date
class(email1$event_date) # to check data type (date)
email1 <- email1 %>% mutate(event_date=factor(format(event_date, format="%m-%d")))

email1 <- email1 %>% mutate(finish_survey = (users_completing_survey / users_starting_survey)*100,
                            complete_convert = (users_converting / users_completing_survey)*100,
                            start_convert = (users_converting / users_starting_survey)*100)

email1
```

# Data Dictionary
Variable                 Description
------------------------ ------------
event_date               Date on which the event took place
users_starting_survey    The number of users who started the survey
users_completing_survey  The number of users who completed the survey
users_converting         The number of users who completed an order
finish_survey            The number of users who completed the survey to the number of users who started the survey ratio 
complete_convert         The number of users who completed an order to the number of users who completed the survey ratio
start_convert            The number of users who completed an order to the number of users who started the survey ratio

# Graph
## % of Survey Completion Customers per Start
## # of Completing Survey Customers
## % of Conversion per Survey Completion
```{r}
sur_fin <- ggplot(email1, aes(x=event_date, y=finish_survey)) + 
           geom_line(group=1) + 
           scale_y_continuous(breaks = seq(40, 70, 5)) + 
           theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), axis.title.y=element_blank()) + 
           geom_vline(xintercept = email1$event_date[19], color="red", linetype=1) + 
           labs(x="Date") + 
           ggtitle("% of Survey Completion Customers per Start")

sur_com <- ggplot(email1, aes(x=event_date, y=users_completing_survey)) + 
           geom_line(group=1) + 
           scale_y_continuous(breaks = seq(1100, 2000, 100)) + 
           theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), axis.title.y=element_blank()) + 
           geom_vline(xintercept = email1$event_date[19], color="red", linetype=1) + 
           labs(x="Date") + 
           ggtitle("# of Completing Survey Customers")

com_cov <- ggplot(email1, aes(x=event_date, y=complete_convert)) + 
           geom_line(group=1) + 
           scale_y_continuous(breaks = seq(4, 6, 0.1)) + 
           theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), axis.title.y=element_blank()) + 
           geom_vline(xintercept = email1$event_date[19], color="red", linetype=1) + 
           labs(x="Date") + 
           ggtitle("% of Conversion per Survey Completion")

sur_fin
sur_com
com_cov
```

## Conversion After Survey Start vs Completion
```{r}
gg <- ggplot(email1, aes(x=event_date))

gg +
  geom_line(aes(y=start_convert), color="forest green", group=1) + 
  geom_line(aes(y=complete_convert), color="purple", group=1) + 
  geom_vline(xintercept = email1$event_date[19], color="red", linetype=1) + 
  labs(x="Date") + 
  scale_y_continuous("% of Conversion After Starting Survey", sec.axis = sec_axis(~./1, name="% of Conversion After Completing Survey"), breaks = seq(2, 7, 0.3)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5), axis.title.y.left=element_text(angle=90, colour="forest green"), axis.title.y.right=element_text(angle=90, colour="purple")) + 
  ggtitle("Conversion After Survey Start vs Completion")

# It is obvious that conversion rate after completing survey is always higher than after starting survey since the number of users who started the survey is always higher than that of users who completed the survey.
```